---
title: "INS_basal_ng_IEQ vs. Race, Pairwise comparisons"
author: "Hakmook Kang and Ke Xu <br><small>Department of Biostatistics<br>Vanderbilt University School of Medicine</small>"
date: "<small>`r Sys.Date()`</small>"
knit: (function(inputFile, encoding) { 
      out_dir <- '/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/REPORTS';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(out_dir, paste0('/Reports-Multiple-PairwiseComparisons-AncestryGroups-',Sys.Date(),'.html'))) })
output: 
  html_document:
    theme: paper
    toc: yes
    toc_depth: 5
    toc_float: 
      collapsed: yes
    number_sections: true
---

<style type="text/css">
#TOC{
position:fixed;
top:0;
right:0;
margin: 40px 40px 40px 40px;
background-color: #F0F0F0;
border-color: Black;
z-index: 9;
}
#toc-toggle{
position:fixed;
top:0;
right:0;
margin: 5px 20px 5px 20px;
}
.col-md-3 {
  width: 3%;
}
div.container-fluid.main-container{
  max-width: none;
  margin-left: none;
  margin-right: none;
}
p img{
  max-width:none;
}
.title{
  max-width:100ex;
}
h1.title {
  font-size: 22px;
  color: Black;
}
h1 { /* Header 1 */
  font-size: 18px;
  color: Black;
}
h2 { /* Header 2 */
  font-size: 18px;
  color: Black;
}
h3 { /* Header 3 */
  font-size: 18px;
  color: Black;
}
h4 { /* Header 4 */
   font-size: 16px;
  color: Black;
}
h5 { /* Header 5 */
   font-size: 16px;
  color: Black;
}
hr {
  border-color: Black;
  width:100%;
  border-width:2px;
}
</style>

<button id="toc-toggle" type="button" class="btn btn-default btn-xs code-folding-btn pull-right collapsed" 
onclick="toggletoc()"><span>Table of Contents</span></button>

<script>
function toggletoc(){
$("#TOC").toggle();
}
</script>

<hr>

# Overview

<!-- -->
## Methods

We conducted multiple pairwise comparisons of basal insulin (INS.basal..ng.IEQ.) levels across four ancestry groups.

- SuperPopulationClass (N=268):
  
  - AFR (N=21)
  - AMR (N=86)
  - EAS (N=11)
  - EUR (N=150)


To evaluate differences in basal insulin across ancestry groups, we applied the Wilcoxon rank-sum test for pairwise comparisons. The false discovery rate (FDR) adjustment was used to control for multiple comparisons.

**Results**

P-values < 0.05 were bolded in the results table for emphasis.

```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(error = FALSE)
```

```{r, packages, message=FALSE, echo=FALSE, warning=FALSE}
rm(list=ls())
library(tidyverse)
library(Hmisc)
library(rms)
library(kableExtra)
library(knitr)
library(dplyr)
library(readxl)
library(VGAM)
library(sjPlot)
options(digits = 4)
options(scipen = -3)
```

```{r}
# Define the function for p-values calculations
comput = function(race1, race2, dat1){
  temp1 = dat1$INS_basal_ng_IEQ[dat1[[race1]] == 1]
  temp2 = dat1$INS_basal_ng_IEQ[dat1[[race2]] == 1]
    
  test1 = wilcox.test(temp1, temp2)
 
  pval = c(race1, race2, round(test1$p.value, 4))
  return(pval)
}
```

```{r, results= "hide", warning=FALSE, message=FALSE}
# Data cleaning
hipp<-read_excel("/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA0/20240411_HIPP_data_freeze_202211071_new_morphology_data_updated.xlsx", sheet="Master_table")

# Replace spaces, parentheses, dashes, and other special characters with underscores
colnames(hipp) <- gsub("[^[:alnum:]]+", "_", colnames(hipp))
colnames(hipp) <- gsub("_+", "_", colnames(hipp))
colnames(hipp) <- gsub("^_|_$", "", colnames(hipp))
colnames(hipp) <- gsub("content", "percent", colnames(hipp))


hipp = hipp[which(hipp$n299cohort == "Y"),]

# define non-diabetes and pre-diabetes

hipp$group<-NA
hipp$group[hipp$Donor_HbA1c<5.7]<-1
hipp$group[hipp$Donor_HbA1c>=5.7]<-2
hipp$group<-factor(hipp$group, levels = 1:2, labels = c("Normal","Pre-diabetes"))

#redefine race to combine American Indian with Native Hawaiian/Pacific Islander
hipp$race2<-NA
hipp$race2[hipp$Race=="White"]<-1
hipp$race2[hipp$Race=="Black or African American"]<-2
hipp$race2[hipp$Race=="Hispanic/Latino"]<-3
hipp$race2[hipp$Race=="Asian"]<-4
# hipp$race2[hipp$Race=="American Indian or Alaska Native" | 
#              hipp$Race=="Native Hawaiian or Other Pacific Islander"]<-5
# hipp$race2[hipp$Race=="Not Available"]<-6
hipp$race2<-factor(hipp$race2, levels = 1:4, 
                   labels = c("White","Black","Hispanic","Asian"))
label(hipp$race2) = "Race"

hipp<-subset(hipp, subset = !is.na(race2))

hipp$center<-NA
hipp$center[hipp$Center=="Scharp-Lacy"]<-1
hipp$center[hipp$Center=="SC-ICRC"]<-2
hipp$center[hipp$Center=="Miami"]<-3
hipp$center[hipp$Center=="Wisconsin"]<-4
hipp$center[hipp$Center=="Pennsylvania"]<-5
hipp$center<-factor(hipp$center, levels = 1:5, labels = c("Scharp-Lacy","SC-ICRC","Miami","Wisconsin","Pennsylvania"))

hipp$Center<-factor(hipp$Center)
hipp$Race<-factor(hipp$Race)
hipp$White = factor(ifelse(hipp$race2 == "White", 1, 0))
hipp$Black = factor(ifelse(hipp$race2 == "Black", 1, 0))
hipp$Hispanic = factor(ifelse(hipp$race2 == "Hispanic", 1, 0))
hipp$Asian = factor(ifelse(hipp$race2 == "Asian", 1, 0))

hipp$INS_basal_ng_IEQ<-scale(as.numeric(hipp$INS_basal_ng_IEQ))

# Read Genetic data
gen_dat = read.csv('/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA0/IIDP_for_Yasminye_71924_HK.csv')

hipp$DONOR_RRID = substring(hipp$RRID,6)
dat_all = merge(gen_dat, hipp, by="DONOR_RRID")

### genetic ancestry
#names(dat_all)
dat_all$AFR = factor(ifelse(dat_all$SuperPopulationClass == "AFR", 1, 0))
dat_all$AMR = factor(ifelse(dat_all$SuperPopulationClass == "AMR", 1, 0))
dat_all$EAS = factor(ifelse(dat_all$SuperPopulationClass == "EAS", 1, 0))
dat_all$EUR = factor(ifelse(dat_all$SuperPopulationClass == "EUR", 1, 0))
```


# INS_basal_ng_IEQ: genetic ancestry

```{r,  warning=FALSE}
############################################################

out1 = comput("EUR", "AFR", dat_all)
out2 = comput("EUR", "EAS", dat_all)
out3 = comput("EUR", "AMR", dat_all)
out4 = comput("AFR", "EAS", dat_all)
out5 = comput("AFR", "AMR", dat_all)
out6 = comput("EAS", "AMR", dat_all)

outnew = data.frame(rbind(out1, out2, out3, out4, out5, out6))
colnames(outnew) = c("race1", "race2", "P_Value")

outnew$Adjust_P_Value = p.adjust(as.numeric(outnew$P_Value), method="fdr")
rownames(outnew) = NULL

  # Convert P_Value and Adjust_P_Value columns to numeric
  data <- outnew %>%
    mutate(
      P_Value = as.numeric(P_Value),
      Adjust_P_Value = as.numeric(Adjust_P_Value)
    )
  
  # Format p-values and adjusted p-values as scientific notation
  data$pvalueCharacter <- as.character(formatC(data$P_Value, digits = 4, format = 'f'))
  data$adjpvalueCharacter <- as.character(formatC(data$Adjust_P_Value, digits = 4, format = 'f'))
  
  # Apply bold formatting for p-values less than 0.05
  data[data$P_Value < 0.05, 'pvalueCharacter'] <- cell_spec(data[data$P_Value < 0.05, 'pvalueCharacter'], "html", bold = TRUE)
  data[data$Adjust_P_Value < 0.05, 'adjpvalueCharacter'] <- cell_spec(data[data$Adjust_P_Value < 0.05, 'adjpvalueCharacter'], "html", bold = TRUE)
  
  # Drop the original P_Value and Adjust_P_Value columns
  data <- data[, -c(3, 4)]
  
  # Rename the columns
  colnames(data) <- c("Race1", "Race2", "P-val", "Adj P-val")
  
  # Return the styled table
  kbl(data, escape = FALSE, digits = 4) %>%
    kable_styling()
```

