---
title: "Histograms and density plots for insulin & glucagon traits (scaled / no scaled)"
author: "Hakmook Kang and Ke Xu <br><small>Department of Biostatistics<br>Vanderbilt University School of Medicine</small>"
date: "<small>`r Sys.Date()`</small>"
knit: (function(inputFile, encoding) { 
      out_dir <- '/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/REPORTS';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(out_dir, paste0('/Reports-Histogram-Density-',Sys.Date(),'.html'))) })
output: 
  html_document:
    code_folding: hide
    theme: paper
    toc: yes
    toc_depth: 5
    toc_float: true
    number_sections: true
    df_print: paged
editor_options: 
  chunk_output_type: inline
description: "for Marcela"
---

<style type="text/css">
#TOC{
position:fixed;
top:0;
right:0;
margin: 40px 40px 40px 40px;
background-color: #F0F0F0;
border-color: Black;
z-index: 9;
}
#toc-toggle{
position:fixed;
top:0;
right:0;
margin: 5px 20px 5px 20px;
}
.col-md-3 {
  width: 3%;
}
div.container-fluid.main-container{
  max-width: none;
  margin-left: none;
  margin-right: none;
}
p img{
  max-width:none;
}
.title{
  max-width:100ex;
}
h1.title {
  font-size: 22px;
  color: Black;
}
h1 { /* Header 1 */
  font-size: 18px;
  color: Black;
}
h2 { /* Header 2 */
  font-size: 18px;
  color: Black;
}
h3 { /* Header 3 */
  font-size: 18px;
  color: Black;
}
h4 { /* Header 4 */
   font-size: 16px;
  color: Black;
}
h5 { /* Header 5 */
   font-size: 16px;
  color: Black;
}
hr {
  border-color: Black;
  width:100%;
  border-width:2px;
}
</style>

<button id="toc-toggle" type="button" class="btn btn-default btn-xs code-folding-btn pull-right collapsed" 
onclick="toggletoc()"><span>Table of Contents</span></button>

<script>
function toggletoc(){
$("#TOC").toggle();
}
</script>

<hr>



```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(error = FALSE)
```

```{r, packages, message=FALSE, echo=FALSE, warning=FALSE}
rm(list=ls())
library(tidyverse)
library(Hmisc)
library(rms)
library(kableExtra)
library(knitr)
library(dplyr)
#library(xlsx)
library(VGAM)
library(sjPlot)
library(readxl)
library(ggplot2)
library(gridExtra)
options(digits = 4)
```


# Overview

<!-- -->
## Results

Histograms and density plots for insulin \& glucagon secretion traits.

A list of insulin traits variable:

- Quantitative (ng/IEQ):

  - INS_basal_ng_IEQ
  - INS_1st_AUC_ng_IEQ
  - INS_2nd_AUC_ng_IEQ
  - INS_G_16_7_AUC_ng_IEQ
  - INS_G_16_7_SI
  - INS_G_16_7_IBMX_100_AUC_ng_IEQ
  - INS_G_16_7_IBMX_100_SI
  - INS_G_1_7_Epi_1_AUC_ng_IEQ
  - INS_G_1_7_Epi_1_II_updated
  - INS_KCl_20_AUC_ng_IEQ
  - INS_KCl_20_SI 


A list of glucagon traits variable:

- Quantitative (pg/IEQ):
  
  - GCG_basal_pg_IEQ
  - GCG_G_16_7_AUC_pg_IEQ
  - GCG_G_16_7_II
  - GCG_G_16_7_IBMX_100_AUC_pg_IEQ
  - GCG_G_16_7_IBMX_100_SI
  - GCG_G_1_7_Epi_1_AUC_pg_IEQ
  - GCG_G_1_7_Epi_1_SI
  - GCG_KCl_20_AUC_pg_IEQ
  - GCG_KCl_20_SI 

  
***
```{r}
# Define the function for formatting tables
format_summary_table <- function(data) {
  
  # Convert P_Value and Adjust_P_Value columns to numeric
  data <- data %>%
    mutate(
      P_Value = as.numeric(P_Value),
      Adjust_P_Value = as.numeric(Adjust_P_Value)
    )
  
  # Format p-values and adjusted p-values as scientific notation
  data$pvalueCharacter <- as.character(formatC(data$P_Value, digits = 3, format = 'e'))
  data$adjpvalueCharacter <- as.character(formatC(data$Adjust_P_Value, digits = 3, format = 'e'))
  
  # Apply bold formatting for p-values less than 0.05
  data[data$P_Value < 0.05, 'pvalueCharacter'] <- cell_spec(data[data$P_Value < 0.05, 'pvalueCharacter'], "html", bold = TRUE)
  data[data$Adjust_P_Value < 0.05, 'adjpvalueCharacter'] <- cell_spec(data[data$Adjust_P_Value < 0.05, 'adjpvalueCharacter'], "html", bold = TRUE)
  
  # Drop the original P_Value and Adjust_P_Value columns
  data <- data[, -c(2, 3)]
  
  # Rename the columns
  colnames(data) <- c("Coeff", "P-val", "Adj P-val")
  
  # Return the styled table
  kbl(data, escape = FALSE, digits = 4) %>%
    kable_styling()
}
```


```{r, results= "hide", warning=FALSE}
## 5-3-2024, update the previous version after Yasminye updated the master data set.
## 7-31-2024 scale all variables

hipp<-read_excel("/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA0/20240411_HIPP_data_freeze_202211071_new_morphology_data_updated.xlsx", sheet="Master_table")

# Replace spaces, parentheses, dashes, and other special characters with underscores
colnames(hipp) <- gsub("[^[:alnum:]]+", "_", colnames(hipp))
colnames(hipp) <- gsub("_+", "_", colnames(hipp))
colnames(hipp) <- gsub("^_|_$", "", colnames(hipp))
colnames(hipp) <- gsub("content", "percent", colnames(hipp))


hipp = hipp[which(hipp$n299cohort == "Y"),]

# define non-diabetes and pre-diabetes

hipp$group<-NA
hipp$group[hipp$Donor_HbA1c<5.7]<-1
hipp$group[hipp$Donor_HbA1c>=5.7]<-2
hipp$group<-factor(hipp$group, levels = 1:2, labels = c("Normal","Pre-diabetes"))

#redefine race to combine American Indian with Native Hawaiian/Pacific Islander
hipp$race2<-NA
hipp$race2[hipp$Race=="White"]<-1
hipp$race2[hipp$Race=="Black or African American"]<-2
hipp$race2[hipp$Race=="Hispanic/Latino"]<-3
hipp$race2[hipp$Race=="Asian"]<-4
# hipp$race2[hipp$Race=="American Indian or Alaska Native" | 
#              hipp$Race=="Native Hawaiian or Other Pacific Islander"]<-5
# hipp$race2[hipp$Race=="Not Available"]<-6
hipp$race2<-factor(hipp$race2, levels = 1:4, 
                   labels = c("White","Black","Hispanic","Asian"))
label(hipp$race2) = "Race"

hipp<-subset(hipp, subset = !is.na(race2))  # dim(hipp)[1]  321

hipp$center<-NA
hipp$center[hipp$Center=="Scharp-Lacy"]<-1
hipp$center[hipp$Center=="SC-ICRC"]<-2
hipp$center[hipp$Center=="Miami"]<-3
hipp$center[hipp$Center=="Wisconsin"]<-4
hipp$center[hipp$Center=="Pennsylvania"]<-5
hipp$center<-factor(hipp$center, levels = 1:5, labels = c("Scharp-Lacy","SC-ICRC","Miami","Wisconsin","Pennsylvania"))

hipp$Center<-factor(hipp$Center)
hipp$Race<-factor(hipp$Race)
```


```{r}
INS_vars <- c("INS_basal_ng_IEQ", "INS_1st_AUC_ng_IEQ", "INS_2nd_AUC_ng_IEQ", 
  "INS_G_16_7_AUC_ng_IEQ", "INS_G_16_7_SI", "INS_G_16_7_IBMX_100_AUC_ng_IEQ", 
  "INS_G_16_7_IBMX_100_SI", "INS_G_1_7_Epi_1_AUC_ng_IEQ", "INS_G_1_7_Epi_1_II_updated", 
  "INS_KCl_20_AUC_ng_IEQ", "INS_KCl_20_SI")

GCG_vars <- c("GCG_basal_pg_IEQ", "GCG_G_16_7_AUC_pg_IEQ", "GCG_G_16_7_II", 
  "GCG_G_16_7_IBMX_100_AUC_pg_IEQ", "GCG_G_16_7_IBMX_100_SI", 
  "GCG_G_1_7_Epi_1_AUC_pg_IEQ", "GCG_G_1_7_Epi_1_SI", "GCG_KCl_20_AUC_pg_IEQ", 
  "GCG_KCl_20_SI")
```

# Histogram and Density Plots
## Insulin Traits Variable 
### Before scaled
```{r fig.width=10, fig.height=10}
# Generate histogram and density plots
plot_list <- lapply(INS_vars, function(var) {
  ggplot(hipp, aes_string(x = var)) +
    geom_histogram(aes(y = ..density..), bins = 30, fill = "skyblue", color = "black", alpha = 0.6) +
    geom_density(color = "darkblue", size = 1) +
    labs(title = var, x = NULL, y = "Density") +
    theme_minimal()
})

# Arrange the plots in a grid (adjust 'ncol' based on how many columns you want)
grid.arrange(grobs = plot_list, ncol = 3)
```

### After scaled
```{r fig.width=10, fig.height=10}
# Scale INS variables
hipp[INS_vars] <- lapply(hipp[INS_vars], function(x) scale(as.numeric(x)))
# Generate histogram and density plots
plot_list <- lapply(INS_vars, function(var) {
  ggplot(hipp, aes_string(x = var)) +
    geom_histogram(aes(y = ..density..), bins = 30, fill = "skyblue", color = "black", alpha = 0.6) +
    geom_density(color = "darkblue", size = 1) +
    labs(title = var, x = NULL, y = "Density") +
    theme_minimal()
})

# Arrange the plots in a grid (adjust 'ncol' based on how many columns you want)
grid.arrange(grobs = plot_list, ncol = 3)
```

## Glucagon Traits Variable 
### Before scaled
```{r fig.width=10, fig.height=10}
# Generate histogram and density plots
plot_list <- lapply(GCG_vars, function(var) {
  ggplot(hipp, aes_string(x = var)) +
    geom_histogram(aes(y = ..density..), bins = 30, fill = "skyblue", color = "black", alpha = 0.6) +
    geom_density(color = "darkblue", size = 1) +
    labs(title = var, x = NULL, y = "Density") +
    theme_minimal()
})

# Arrange the plots in a grid (adjust 'ncol' based on how many columns you want)
grid.arrange(grobs = plot_list, ncol = 3)
```

### After scaled
```{r fig.width=10, fig.height=10}
# Scale GCG variables
hipp[GCG_vars] <- lapply(hipp[GCG_vars], function(x) scale(as.numeric(x)))
# Generate histogram and density plots
plot_list <- lapply(GCG_vars, function(var) {
  ggplot(hipp, aes_string(x = var)) +
    geom_histogram(aes(y = ..density..), bins = 30, fill = "skyblue", color = "black", alpha = 0.6) +
    geom_density(color = "darkblue", size = 1) +
    labs(title = var, x = NULL, y = "Density") +
    theme_minimal()
})

# Arrange the plots in a grid (adjust 'ncol' based on how many columns you want)
grid.arrange(grobs = plot_list, ncol = 3)
```
