---
title: "Correlation between islet morphological variables and insulin & glucagon traits (scaled)"
author: "Hakmook Kang and Ke Xu <br><small>Department of Biostatistics<br>Vanderbilt University School of Medicine</small>"
date: "<small>`r Sys.Date()`</small>"
knit: (function(inputFile, encoding) { 
      out_dir <- '/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/REPORTS';
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(out_dir, paste0('/Reports-Models-',Sys.Date(),'.html'))) })
output: 
  html_document:
    code_folding: hide
    theme: paper
    toc: yes
    toc_depth: 5
    toc_float: true
    number_sections: true
    df_print: paged
editor_options: 
  chunk_output_type: inline
description: "for Marcela"
---

<style type="text/css">
#TOC{
position:fixed;
top:0;
right:0;
margin: 40px 40px 40px 40px;
background-color: #F0F0F0;
border-color: Black;
z-index: 9;
}
#toc-toggle{
position:fixed;
top:0;
right:0;
margin: 5px 20px 5px 20px;
}
.col-md-3 {
  width: 3%;
}
div.container-fluid.main-container{
  max-width: none;
  margin-left: none;
  margin-right: none;
}
p img{
  max-width:none;
}
.title{
  max-width:100ex;
}
h1.title {
  font-size: 22px;
  color: Black;
}
h1 { /* Header 1 */
  font-size: 18px;
  color: Black;
}
h2 { /* Header 2 */
  font-size: 18px;
  color: Black;
}
h3 { /* Header 3 */
  font-size: 18px;
  color: Black;
}
h4 { /* Header 4 */
   font-size: 16px;
  color: Black;
}
h5 { /* Header 5 */
   font-size: 16px;
  color: Black;
}
hr {
  border-color: Black;
  width:100%;
  border-width:2px;
}
</style>

<button id="toc-toggle" type="button" class="btn btn-default btn-xs code-folding-btn pull-right collapsed" 
onclick="toggletoc()"><span>Table of Contents</span></button>

<script>
function toggletoc(){
$("#TOC").toggle();
}
</script>

<hr>



```{r, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
knitr::opts_chunk$set(error = FALSE)
```

```{r, packages, message=FALSE, echo=FALSE, warning=FALSE}
rm(list=ls())
library(tidyverse)
library(Hmisc)
library(rms)
library(kableExtra)
library(knitr)
library(dplyr)
#library(xlsx)
library(VGAM)
library(sjPlot)
library(readxl)
options(digits = 4)
```


# Overview

<!-- -->
## Methods

Assessing correlation between morphological variables and insulin \& glucagon secretion traits.

For each morphology variable, we fit 20 regression models, i.e., 20 insulin (N=11) and glucagon (N=9) secretion trait variables. The sample size will be much smaller than n=299 due to lots of missing information in morphological variables.We controlled 8 covariates. 

A list of morphological variable:

- islet diameter preperi
- islet area preperi
- islet perimeter preperi
- islet diameter postperi
- islet area postperi
- islet perimeter postperi
- islet diameter 
- islet area 
- islet perimeter 

A list of insulin traits variable:

- Quantitative (ng/IEQ):

  - INS_basal_ng_IEQ
  - INS_1st_AUC_ng_IEQ
  - INS_2nd_AUC_ng_IEQ
  - INS_G_16_7_AUC_ng_IEQ
  - INS_G_16_7_SI
  - INS_G_16_7_IBMX_100_AUC_ng_IEQ
  - INS_G_16_7_IBMX_100_SI
  - INS_G_1_7_Epi_1_AUC_ng_IEQ
  - INS_G_1_7_Epi_1_II_updated
  - INS_KCl_20_AUC_ng_IEQ
  - INS_KCl_20_SI 

A list of glucagon traits variable:

- Quantitative (pg/IEQ):
  
  - GCG_basal_pg_IEQ
  - GCG_G_16_7_AUC_pg_IEQ
  - GCG_G_16_7_II
  - GCG_G_16_7_IBMX_100_AUC_pg_IEQ
  - GCG_G_16_7_IBMX_100_SI
  - GCG_G_1_7_Epi_1_AUC_pg_IEQ
  - GCG_G_1_7_Epi_1_SI
  - GCG_KCl_20_AUC_pg_IEQ
  - GCG_KCl_20_SI 
  
**Models(scaled)**

outcome ~ insulin & glucagon traits + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + PreShipmentCultureTime + IsletTransitTime

**Results**

The adjusted p-values were computed using the false discovery rate (FDR) method to correct for multiple comparisons.
               
***
```{r}
# Define the function for formatting tables
format_summary_table <- function(data) {
  
  # Convert P_Value and Adjust_P_Value columns to numeric
  data <- data %>%
    mutate(
      P_Value = as.numeric(P_Value),
      Adjust_P_Value = as.numeric(Adjust_P_Value)
    )
  
  # Format p-values and adjusted p-values as scientific notation
  data$pvalueCharacter <- as.character(formatC(data$P_Value, digits = 3, format = 'e'))
  data$adjpvalueCharacter <- as.character(formatC(data$Adjust_P_Value, digits = 3, format = 'e'))
  
  # Apply bold formatting for p-values less than 0.05
  data[data$P_Value < 0.05, 'pvalueCharacter'] <- cell_spec(data[data$P_Value < 0.05, 'pvalueCharacter'], "html", bold = TRUE)
  data[data$Adjust_P_Value < 0.05, 'adjpvalueCharacter'] <- cell_spec(data[data$Adjust_P_Value < 0.05, 'adjpvalueCharacter'], "html", bold = TRUE)
  
  # Drop the original P_Value and Adjust_P_Value columns
  data <- data[, -c(2, 3)]
  
  # Rename the columns
  colnames(data) <- c("Coeff", "P-val", "Adj P-val")
  
  # Return the styled table
  kbl(data, escape = FALSE, digits = 4) %>%
    kable_styling()
}
```


```{r, results= "hide", warning=FALSE}
hipp<-read_excel("/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA0/20240411_HIPP_data_freeze_202211071_new_morphology_data_updated.xlsx", sheet="Master_table")

# Replace spaces, parentheses, dashes, and other special characters with underscores
colnames(hipp) <- gsub("[^[:alnum:]]+", "_", colnames(hipp))
colnames(hipp) <- gsub("_+", "_", colnames(hipp))
colnames(hipp) <- gsub("^_|_$", "", colnames(hipp))
colnames(hipp) <- gsub("content", "percent", colnames(hipp))


hipp = hipp[which(hipp$n299cohort == "Y"),]

# define non-diabetes and pre-diabetes
hipp$group<-NA
hipp$group[hipp$Donor_HbA1c<5.7]<-1
hipp$group[hipp$Donor_HbA1c>=5.7]<-2
hipp$group<-factor(hipp$group, levels = 1:2, labels = c("Normal","Pre-diabetes"))

#redefine race to combine American Indian with Native Hawaiian/Pacific Islander
hipp$race2<-NA
hipp$race2[hipp$Race=="White"]<-1
hipp$race2[hipp$Race=="Black or African American"]<-2
hipp$race2[hipp$Race=="Hispanic/Latino"]<-3
hipp$race2[hipp$Race=="Asian"]<-4
hipp$race2<-factor(hipp$race2, levels = 1:4, 
                   labels = c("White","Black","Hispanic","Asian"))
label(hipp$race2) = "Race"

hipp<-subset(hipp, subset = !is.na(race2))  # dim(hipp)[1]  321

hipp$Race<-factor(hipp$Race)
```


```{r}
INS_vars <- c("INS_basal_ng_IEQ", "INS_1st_AUC_ng_IEQ", "INS_2nd_AUC_ng_IEQ", 
  "INS_G_16_7_AUC_ng_IEQ", "INS_G_16_7_SI", "INS_G_16_7_IBMX_100_AUC_ng_IEQ", 
  "INS_G_16_7_IBMX_100_SI", "INS_G_1_7_Epi_1_AUC_ng_IEQ", "INS_G_1_7_Epi_1_II_updated", 
  "INS_KCl_20_AUC_ng_IEQ", "INS_KCl_20_SI")

GCG_vars <- c("GCG_basal_pg_IEQ", "GCG_G_16_7_AUC_pg_IEQ", "GCG_G_16_7_II", 
  "GCG_G_16_7_IBMX_100_AUC_pg_IEQ", "GCG_G_16_7_IBMX_100_SI", 
  "GCG_G_1_7_Epi_1_AUC_pg_IEQ", "GCG_G_1_7_Epi_1_SI", "GCG_KCl_20_AUC_pg_IEQ", 
  "GCG_KCl_20_SI")


# Scale INS variables
hipp[INS_vars] <- lapply(hipp[INS_vars], function(x) scale(as.numeric(x)))

# Scale GCG variables
hipp[GCG_vars] <- lapply(hipp[GCG_vars], function(x) scale(as.numeric(x)))


# morphological variables: need to convert them to numeric
morpho_vars <- c("Islet_diameter_preperi", "Islet_area_preperi", "Islet_perimeter_preperi",
                 "Islet_diameter_postperi", "Islet_area_postperi", "Islet_perimeter_postperi",
                 "Islet_diameter", "Islet_area", "Islet_perimeter")

hipp[morpho_vars] <- lapply(hipp[morpho_vars], function(x) scale(as.numeric(x)))


# Scale covariates
hipp$PreShipmentCultureTime<-scale(hipp$Pre_shipment_Culture_Time_hours)
hipp$IsletTransitTime<-scale(hipp$Islet_Transit_Time_hours)
hipp$Age_years = scale(hipp$Age_years)
hipp$BMI = scale(hipp$BMI)
hipp$Donor_HbA1c = scale(hipp$Donor_HbA1c)

hipp$center<-NA
hipp$center[hipp$Center=="Scharp-Lacy"]<-1
hipp$center[hipp$Center=="SC-ICRC"]<-2
hipp$center[hipp$Center=="Miami"]<-3
hipp$center[hipp$Center=="Wisconsin"]<-4
hipp$center[hipp$Center=="Pennsylvania"]<-5
hipp$center<-factor(hipp$center, levels = 1:5, labels = c("Scharp-Lacy","SC-ICRC","Miami","Wisconsin","Pennsylvania"))
```

```{r, results= "hide", warning=FALSE}
###################################################################
###################################################################
###################################################################
vars_int = morpho_vars
outcome_int_ins = INS_vars
outcome_int_glu = GCG_vars

Summary_Table = vector(mode='list', length=length(vars_int))
model_out = vector(mode='list', length=length(vars_int))
names(model_out) = vars_int
for (m in 1:length(vars_int)){
  temp_summary = NULL
  for (k in 1:length(outcome_int_ins)){
    model = as.formula(paste0(outcome_int_ins[k], "~", vars_int[m], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
    fit = lm(model, data = hipp)
    temp = summary(fit)
    temp1 = temp$coefficients[2,]
    temp1[2:3] = round(temp1[2:3], 4)
    temp1[c(1,4)] = formatC(temp1[c(1,4)], format = "e", digits = 3)
    temp_summary = rbind(temp_summary, temp1) 
    
    model_out[[m]][[k]] = summary(fit)
  }
  names(model_out[[m]]) = vars_int
  
  temp_summary = as.data.frame(temp_summary)
  temp_summary$adj_pvalue = formatC(p.adjust(temp_summary[,4], method='fdr'),
  format = "e", digits = 3)
  Summary_Table[[vars_int[m]]] = temp_summary
}

############################################
### Glucagon Secretion
########################################

Summary_Table_g = vector(mode='list', length=length(vars_int))
model_out_g = vector(mode='list', length=length(vars_int))
names(model_out_g) = vars_int
for (m in 1:length(vars_int)){
  temp_summary = NULL
  for (k in 1:length(outcome_int_glu)){
    model = as.formula(paste0(outcome_int_glu[k], "~", vars_int[m], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
    fit = lm(model, data = hipp)
    temp = summary(fit)
    temp1 = temp$coefficients[2,]
    temp1[2:3] = round(temp1[2:3], 4)
    temp1[c(1,4)] = formatC(temp1[c(1,4)], format = "e", digits = 3)
    temp_summary = rbind(temp_summary, temp1) 
    
    model_out_g[[m]][[k]] = summary(fit)
  }
  names(model_out_g[[m]]) = vars_int
  
  temp_summary = as.data.frame(temp_summary)
  temp_summary$adj_pvalue = formatC(p.adjust(temp_summary[,4], method='fdr'),
  format = "e", digits = 3)
  Summary_Table_g[[vars_int[m]]] = temp_summary
}

```


# Results

## Islet Diameter Preperi

### Insuline secretion

```{r warning=FALSE, message=FALSE}
vars_int_index <- which(vars_int == "Islet_diameter_preperi")

modlist <- lapply(1:length(outcome_int_ins),function(i){
  model = as.formula(paste0(outcome_int_ins[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_ins
```

```{r results="asis"}
for (x in outcome_int_ins){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```


### Glucagon secretion

```{r warning=FALSE, message=FALSE}
modlist <- lapply(1:length(outcome_int_glu),function(i){
  model = as.formula(paste0(outcome_int_glu[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_glu
```

```{r results="asis"}
for (x in outcome_int_glu){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```


## Islet Area Preperi

### Insuline secretion

```{r warning=FALSE, message=FALSE}
vars_int_index <- which(vars_int == "Islet_area_preperi")
modlist <- lapply(1:length(outcome_int_ins),function(i){
  model = as.formula(paste0(outcome_int_ins[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_ins
```

```{r results="asis"}
for (x in outcome_int_ins){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```

### Glucagon secretion

```{r warning=FALSE, message=FALSE}
modlist <- lapply(1:length(outcome_int_glu),function(i){
  model = as.formula(paste0(outcome_int_glu[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_glu
```

```{r results="asis"}
for (x in outcome_int_glu){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```

## Islet Perimeter Preperi

### Insuline secretion

```{r warning=FALSE, message=FALSE}
vars_int_index <- which(vars_int == "Islet_perimeter_preperi")

modlist <- lapply(1:length(outcome_int_ins),function(i){
  model = as.formula(paste0(outcome_int_ins[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_ins
```

```{r results="asis"}
for (x in outcome_int_ins){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```

### Glucagon secretion

```{r warning=FALSE, message=FALSE}

modlist <- lapply(1:length(outcome_int_glu),function(i){
  model = as.formula(paste0(outcome_int_glu[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_glu
```

```{r results="asis"}
for (x in outcome_int_glu){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```


## Islet Diameter Postperi

### Insuline secretion

```{r warning=FALSE, message=FALSE}
vars_int_index <- which(vars_int == "Islet_diameter_postperi")

modlist <- lapply(1:length(outcome_int_ins),function(i){
  model = as.formula(paste0(outcome_int_ins[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_ins
```

```{r results="asis"}
for (x in outcome_int_ins){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```

### Glucagon secretion

```{r warning=FALSE, message=FALSE}

modlist <- lapply(1:length(outcome_int_glu),function(i){
  model = as.formula(paste0(outcome_int_glu[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_glu
```

```{r results="asis"}
for (x in outcome_int_glu){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```


## Islet Area Postperi

### Insuline secretion

```{r warning=FALSE, message=FALSE}
vars_int_index <- which(vars_int == "Islet_area_postperi")

modlist <- lapply(1:length(outcome_int_ins),function(i){
  model = as.formula(paste0(outcome_int_ins[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_ins
```

```{r results="asis"}
for (x in outcome_int_ins){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```

### Glucagon secretion

```{r warning=FALSE, message=FALSE}

modlist <- lapply(1:length(outcome_int_glu),function(i){
  model = as.formula(paste0(outcome_int_glu[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_glu
```

```{r results="asis"}
for (x in outcome_int_glu){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```

## Islet Perimeter Postperi

### Insuline secretion

```{r warning=FALSE, message=FALSE}
vars_int_index <- which(vars_int == "Islet_perimeter_postperi")

modlist <- lapply(1:length(outcome_int_ins),function(i){
  model = as.formula(paste0(outcome_int_ins[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_ins
```

```{r results="asis"}
for (x in outcome_int_ins){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```

### Glucagon secretion

```{r warning=FALSE, message=FALSE}

modlist <- lapply(1:length(outcome_int_glu),function(i){
  model = as.formula(paste0(outcome_int_glu[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_glu
```

```{r results="asis"}
for (x in outcome_int_glu){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```

## Islet Diameter

### Insuline secretion

```{r warning=FALSE, message=FALSE}
vars_int_index <- which(vars_int == "Islet_diameter")

modlist <- lapply(1:length(outcome_int_ins),function(i){
  model = as.formula(paste0(outcome_int_ins[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_ins
```

```{r results="asis"}
for (x in outcome_int_ins){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```

### Glucagon secretion

```{r warning=FALSE, message=FALSE}

modlist <- lapply(1:length(outcome_int_glu),function(i){
  model = as.formula(paste0(outcome_int_glu[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_glu
```

```{r results="asis"}
for (x in outcome_int_glu){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```

## Islet Area

### Insuline secretion

```{r warning=FALSE, message=FALSE}
vars_int_index <- which(vars_int == "Islet_area")

modlist <- lapply(1:length(outcome_int_ins),function(i){
  model = as.formula(paste0(outcome_int_ins[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_ins
```

```{r results="asis"}
for (x in outcome_int_ins){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```

### Glucagon secretion

```{r warning=FALSE, message=FALSE}

modlist <- lapply(1:length(outcome_int_glu),function(i){
  model = as.formula(paste0(outcome_int_glu[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_glu
```

```{r results="asis"}
for (x in outcome_int_glu){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```

## Islet Perimeter

### Insuline secretion

```{r warning=FALSE, message=FALSE}
vars_int_index <- which(vars_int == "Islet_perimeter")

modlist <- lapply(1:length(outcome_int_ins),function(i){
  model = as.formula(paste0(outcome_int_ins[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_ins
```

```{r results="asis"}
for (x in outcome_int_ins){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```

### Glucagon secretion

```{r warning=FALSE, message=FALSE}

modlist <- lapply(1:length(outcome_int_glu),function(i){
  model = as.formula(paste0(outcome_int_glu[i], "~", vars_int[vars_int_index], " + Donor_HbA1c + Gender + race2 + Age_years + center + BMI + 
               PreShipmentCultureTime + IsletTransitTime"))
  mod = lm(model, data = hipp)
  return(mod)
})

names(modlist) = outcome_int_glu
```

```{r results="asis"}
for (x in outcome_int_glu){
  cat(tab_model(modlist[[x]], digits = 4)$knitr,"\n\n--------\n\n")
}
```



# Summary Table

## Islet Diameter Preperi

### Insulin secretion

``` {r}
outcome_var <- 'Islet_diameter_preperi'
rownames(Summary_Table[[outcome_var]]) = outcome_int_ins
write.csv(Summary_Table[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Diameter_preperi_ins_traits_scale.csv')
Summary_Tab = Summary_Table[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_ins
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```

### Glucagon secretion

``` {r}
outcome_var <- 'Islet_diameter_preperi'
rownames(Summary_Table_g[[outcome_var]]) = outcome_int_glu
write.csv(Summary_Table_g[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Diameter_preperi_glucagon_traits_scale.csv')
Summary_Tab = Summary_Table_g[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_glu
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```


## Islet Area Preperi

### Insulin secretion

``` {r}
outcome_var <- "Islet_area_preperi"
rownames(Summary_Table[[outcome_var]]) = outcome_int_ins
write.csv(Summary_Table[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Area_preperi_ins_traits_scale.csv')
Summary_Tab = Summary_Table[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_ins
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```

### Glucagon secretion

``` {r}
outcome_var <- "Islet_area_preperi"
rownames(Summary_Table_g[[outcome_var]]) = outcome_int_glu
write.csv(Summary_Table_g[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Area_preperi_glucagon_traits_scale.csv')
Summary_Tab = Summary_Table_g[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_glu
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```


## Islet Perimeter Preperi

### Insulin secretion

``` {r}
outcome_var <- "Islet_perimeter_preperi"
rownames(Summary_Table[[outcome_var]]) = outcome_int_ins
write.csv(Summary_Table[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Perimeter_preperi_ins_traits_scale.csv')
Summary_Tab = Summary_Table[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_ins
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```

### Glucagon secretion

``` {r}
outcome_var <- "Islet_perimeter_preperi"
rownames(Summary_Table_g[[outcome_var]]) = outcome_int_glu
write.csv(Summary_Table_g[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Perimeter_preperi_glucagon_traits_scale.csv')
Summary_Tab = Summary_Table_g[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_glu
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```


## Islet Diameter Postperi

### Insulin secretion

``` {r}
outcome_var <- "Islet_diameter_postperi"
rownames(Summary_Table[[outcome_var]]) = outcome_int_ins
write.csv(Summary_Table[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Diameter_postperi_ins_traits_scale.csv')
Summary_Tab = Summary_Table[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_ins
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```

### Glucagon secretion

``` {r}
outcome_var <- "Islet_diameter_postperi"
rownames(Summary_Table_g[[outcome_var]]) = outcome_int_glu
write.csv(Summary_Table_g[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Diameter_postperi_glucagon_traits_scale.csv')
Summary_Tab = Summary_Table_g[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_glu
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```


## Islet Area Postperi

### Insulin secretion

``` {r}
outcome_var <- "Islet_area_postperi"
rownames(Summary_Table[[outcome_var]]) = outcome_int_ins
write.csv(Summary_Table[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Area_postperi_ins_traits_scale.csv')
Summary_Tab = Summary_Table[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_ins
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```

### Glucagon secretion

``` {r}
outcome_var <- "Islet_area_postperi"
rownames(Summary_Table_g[[outcome_var]]) = outcome_int_glu
write.csv(Summary_Table_g[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Area_postperi_glucagon_traits_scale.csv')
Summary_Tab = Summary_Table_g[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_glu
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```


## Islet Perimeter Postperi

### Insulin secretion

``` {r}
outcome_var <- "Islet_perimeter_postperi"
rownames(Summary_Table[[outcome_var]]) = outcome_int_ins
write.csv(Summary_Table[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Perimeter_postperi_ins_traits_scale.csv')
Summary_Tab = Summary_Table[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_ins
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```

### Glucagon secretion

``` {r}
outcome_var <- "Islet_perimeter_postperi"
rownames(Summary_Table_g[[outcome_var]]) = outcome_int_glu
write.csv(Summary_Table_g[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Perimeter_postperi_glucagon_traits_scale.csv') # SAVE THE FILES AND SHARE THEM WITH THE TEAM
Summary_Tab = Summary_Table_g[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_glu
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```

## Islet Diameter

### Insulin secretion

``` {r}
outcome_var <- "Islet_diameter"
rownames(Summary_Table[[outcome_var]]) = outcome_int_ins
write.csv(Summary_Table[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Diameter_ins_traits_scale.csv')
Summary_Tab = Summary_Table[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_ins
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```

### Glucagon secretion

``` {r}
outcome_var <- "Islet_diameter"
rownames(Summary_Table_g[[outcome_var]]) = outcome_int_glu
write.csv(Summary_Table_g[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Diameter_glucagon_traits_scale.csv')
Summary_Tab = Summary_Table_g[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_glu
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```


## Islet Area

### Insulin secretion

``` {r}
outcome_var <- "Islet_area"
rownames(Summary_Table[[outcome_var]]) = outcome_int_ins
write.csv(Summary_Table[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Area_ins_traits_scale.csv')
Summary_Tab = Summary_Table[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_ins
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```

### Glucagon secretion

``` {r}
outcome_var <- "Islet_area"
rownames(Summary_Table_g[[outcome_var]]) = outcome_int_glu
write.csv(Summary_Table_g[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Area_glucagon_traits_scale.csv')
Summary_Tab = Summary_Table_g[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_glu
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```


## Islet Perimeter

### Insulin secretion

``` {r}
outcome_var <- "Islet_perimeter"
rownames(Summary_Table[[outcome_var]]) = outcome_int_ins
write.csv(Summary_Table[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Perimeter_ins_traits_scale.csv')
Summary_Tab = Summary_Table[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_ins
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```

### Glucagon secretion

``` {r}
outcome_var <- "Islet_perimeter"
rownames(Summary_Table_g[[outcome_var]]) = outcome_int_glu
write.csv(Summary_Table_g[[outcome_var]], file='/Users/kexu/Library/CloudStorage/OneDrive-VUMC/Research/Active/20241022_HIPP/DATA1/csv_files_scale/Perimeter_glucagon_traits_scale.csv') # SAVE THE FILES AND SHARE THEM WITH THE TEAM
Summary_Tab = Summary_Table_g[[outcome_var]][,-c(2,3)]
colnames(Summary_Tab) = c("Coeff", "P_Value", "Adjust_P_Value")
rownames(Summary_Tab) = outcome_int_glu
formatted_table <- format_summary_table(Summary_Tab);formatted_table
```